Der Titel des Beitrags, der auch etwas länger sein und über zwei Zeilen reichen kann

### 2016-10-13 paper.tex
Convert to UTF-8 and handle bib file with JabRef
Add missing \ after "bzw." to have normal word separation, not sentence separation.
Remove URL tweak as it does not render nice in this template
Include LNI_biblatex in paper.tex - had to disable microtype
Move declaration of \citeauthor to the cbx-file
Fix caption parameter (#7)

%Enable input of umlauts. Change to UTF-8 if you use UTF-8
\usepackage[latin1]{inputenc}

@@

\iflnienglish
\usepackage[figurename=Fig., tablename=Tab., small]{caption}
\else
\usepackage[figurename=Abb., tablename=Tab., small]{caption}
\fi

@@

%for easy quotations: \enquote{text}
\usepackage{csquotes}

@@

%enable margin kerning
\usepackage{microtype}

@@

%tweak \url{...}
\usepackage{url}
%nicer // - solution by http://tex.stackexchange.com/a/98470/9075
\makeatletter
\def\Url@twoslashes{\mathchar`\/\@ifnextchar/{\kern-.2em}{}}
\g@addto@macro\UrlSpecials{\do\/{\Url@twoslashes}}
\makeatother
\urlstyle{same}
%improve wrapping of URLs - hint by http://tex.stackexchange.com/a/10419/9075
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

@@

@@

@@

Formatierung und Abkürzungen werden für die Referenzen \texttt{book}, \texttt{inbook}, \texttt{proceedings}, \texttt{inproceedings}, \texttt{article}, \texttt{online} und \texttt{misc} automatisch vorgenommen.
Mögliche Felder für Referenzen können der Beispieldatei \texttt{paper.bib} entnommen werden.
Andere Referenzen bzw. Felder müssen allenfalls nachträglich angepasst werden.

@@

%DO NOT USE \bibliographystyle - is is already done in lni.cls
%\bibliographystyle{lnig}

>>>>

%Enable input of umlauts using UTF-8.
\usepackage[utf8]{inputenc}

@@

\iflnienglish
\usepackage[figurename=Fig., tablename=Tab., font=small]{caption}
\else
\usepackage[figurename=Abb., tablename=Tab., font=small]{caption}
\fi

@@

@@

@@

%tweak \url{...}
\usepackage{url}
\urlstyle{same}
%improve wrapping of URLs - hint by http://tex.stackexchange.com/a/10419/9075
\makeatletter
\g@addto@macro{\UrlBreaks}{\UrlOrds}
\makeatother

@@

%for easy quotations: \enquote{text}
%also required by biblatex
\usepackage{csquotes}
\usepackage[
  backend=biber,
  style=LNI_biblatex/LNI
]{biblatex}

@@

%enable margin kerning
%currently does not work with pdflatex
%\usepackage{microtype}

@@

Formatierung und Abkürzungen werden für die Referenzen \texttt{book}, \texttt{inbook}, \texttt{proceedings}, \texttt{inproceedings}, \texttt{article}, \texttt{online} und \texttt{misc} automatisch vorgenommen.
Mögliche Felder für Referenzen können der Beispieldatei \texttt{paper.bib} entnommen werden.
Andere Referenzen bzw.\ Felder müssen allenfalls nachträglich angepasst werden.

@@

%No \bibliography{paper} allowed here - biblatex expects it at the preamble
%Run `biber paper` to generate the bibliography
\printbibliography
